Digital Twins for Ocean Robots

### 2024-11-29 paper/paper.tex
final proofreading and edits (part 2)

The core of DTOR is formed by \pkg{OceanRobots.jl}, \pkg{ArgoData.jl}, and \pkg{MeshArrays.jl} for the physical twins, along with \pkg{Climatology.jl}, \pkg{ClimateModels.jl}, \pkg{MITgcm.jl}, and \pkg{Drifters.jl} for the virtual twins (i.e., predictive modeling). The \pkg{ClimateModels.jl} interface streamlines the use of models implemented in various languages. The model hierarchy already includes the models used in this paper, and is easy to extend via pkg{ClimateModels.jl}. DTOR can notably simulate observations in the future based on climate model predictions, and \pkg{ClimateModels.jl} provides two options for this kind of applications -- either querying the CMIP6 archive of model output \cite{CMIP6} or using a fast emulator such as Hector \cite{Hector2015} (Fig.~\ref{fig:globalwarming}).

Within our model hierarchy, future climate scenarios like Fig.~\ref{fig:globalwarming} can be downscaled using gridded climatologies and reanalyses \cite{Forget2010,Forget2015a,Forget2024a}. The ECCO4 and OCCA2 reanalyses are simple to rerun with perturbed surface forcing fields via \pkg{MITgcm.jl}, which is particularly convenient for such applications. Multi-decadal solutions produced in this way can then be further downscaled using km-scale model output (Fig.~\ref{fig:km_scale}). At the end of this modeling workflow, \pkg{OceanRobots.jl}, \pkg{MeshArrays.jl} and \pkg{Drifters.jl} enable calculations such as Figs.~\ref{fig:Argo_Float_simu} and \ref{fig:drifters_speed_simu}, for any of our models. DTOR can also take advantage of gridded satellite data, incl. sea surface temperature and sea level anomalies via \pkg{Climatology.jl}, and it is sometimes possible to use these instead of ocean reanalyses.

@@

Further development of the DTOR framework is expected to proceed in several directions. First, we'd like to integrate additional types of ocean observing platforms, starting with those that do not have a data structure listed yet in Tab.~\ref{tab:robots}. Observational networks that focus on either the coastal ocean, a specific region, or local field experiments could be supported in the future. A top level API to interact with DTOR as a whole through cloud services is also envisioned.

>>>>

The core of DTOR is formed by \pkg{OceanRobots.jl}, \pkg{ArgoData.jl}, and \pkg{MeshArrays.jl} for the physical twins, along with \pkg{Climatology.jl}, \pkg{ClimateModels.jl}, \pkg{MITgcm.jl}, and \pkg{Drifters.jl} for the virtual twins (i.e., predictive modeling). The \pkg{ClimateModels.jl} interface streamlines the use of models implemented in various languages. The model hierarchy already includes models listed in this paper, and is easy to extend via the \pkg{ClimateModels.jl} interface. DTOR can also simulate observations in the future based on climate model predictions (Fig.~\ref{fig:globalwarming}), and \pkg{ClimateModels.jl} provides two options for this kind of applications -- either querying the CMIP6 archive of model output \cite{CMIP6} or using a fast emulator such as Hector \cite{Hector2015}.

Within our model hierarchy, future climate scenarios like Fig.~\ref{fig:globalwarming} can be downscaled using gridded climatologies and reanalyses \cite{Forget2010,Forget2015a,Forget2024a}. The ECCO4 and OCCA2 reanalyses are simple to rerun with perturbed surface forcing fields via \pkg{MITgcm.jl}, which is particularly convenient for such applications. Multi-decadal solutions produced in this way can then be further downscaled using km-scale model output (Fig.~\ref{fig:km_scale}). At the end of this modeling workflow, \pkg{OceanRobots.jl}, \pkg{MeshArrays.jl} and \pkg{Drifters.jl} enable calculations such as Figs.~\ref{fig:Argo_Float_simu} and \ref{fig:drifters_speed_simu}, for any of our models. DTOR can also take advantage of gridded satellite data, incl. sea surface temperature and sea level anomalies via \pkg{Climatology.jl}, which can sometimes be used instead of ocean reanalyses.

@@

Further development of the DTOR framework is expected to proceed in several directions. First, we'd like to integrate additional types of ocean observing platforms, starting with those that do not have a data structure listed yet in Tab.~\ref{tab:robots}. Observational networks that focus on either the coastal ocean, a specific region, or local field experiments could also be supported in the future. In addition, a top level API to interact with DTOR as a whole through cloud services is envisioned and being developed.
